---
title: "Results"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 5
    
    #code_folding: hide
---

```{r setup, include=FALSE, results='hide'}
knitr::opts_chunk$set(cache = TRUE, message = FALSE, results='hide')
```
Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.

# **Scenario**

You are a junior data analyst working in the marketing analyst team at Cyclistic, a bike-share company in Chicago. The director of marketing believes the company’s future success depends on maximizing the number of annual memberships. Therefore,your team wants to understand how casual riders and annual members use Cyclistic bikes differently. From these insights,your team will design a new marketing strategy to convert casual riders into annual members. But first, Cyclistic executives
must approve your recommendations, so they must be backed up with compelling data insights and professional data
visualizations.


## **The What**

**The company’s future success depends on maximizing the number of annual memberships.** 

You are a junior data analyst working in the marketing analyst team at Cyclistic, a bike-share company in Chicago. The director of marketing believes the company’s future success depends on maximizing the number of annual memberships. Therefore,your team wants to understand how casual riders and annual members use Cyclistic bikes differently. From these insights,your team will design a new marketing strategy to convert casual riders into annual members. But first, Cyclistic executives
must approve your recommendations, so they must be backed up with compelling data insights and professional data
visualizations.

## **The Who**

**Therefore,your team wants to understand how casual riders and annual members use Cyclistic bikes differently.**

You are a junior data analyst working in the marketing analyst team at Cyclistic, a bike-share company in Chicago. The director of marketing believes the company’s future success depends on maximizing the number of annual memberships. Therefore,your team wants to understand how casual riders and annual members use Cyclistic bikes differently. From these insights,your team will design a new marketing strategy to convert casual riders into annual members. But first, Cyclistic executives
must approve your recommendations, so they must be backed up with compelling data insights and professional data
visualizations.

```{r, echo=FALSE}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```

## **The When**

```{r, echo=FALSE}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```
